EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
mocking

% Mocking
\TODO{Add some stats on mocking}

>>>>

% Mocking
As mentioned in the previous section, \EVOSUITE now can use private
API access and functional mocking in addition to environment
mocking~\cite{ICST_Mocking17}. In the competition, a total of 20,921
objects were mocked, 1,485 fields were set and 3,090 private methods
were invoked using private API access, and environment classes were
mocked 4,699 times, with \texttt{java.util.Random} and
\texttt{java.io.File} being by far the most frequently mocked
environment classes (resp. 1,286 and 1,121 times). Further
investigation is needed to assess the impact of these mocking features
on test generation effectiveness.
